Tabular Constraint Learning

### 2016-04-14 Paper/ECAI/tabular.tex
Signature changes

\paragraph{Example}
\sergey{need to use this below:}
  For example, a spreadsheet constraint \textit{rank} has \CName \textit{$v_y$ = RANK($v_x$)}, where $v_x$ and $v_y$ are the variables; its \CSignature is: the subgroup assigned to $v_x$ must be numeric, $v_y$ must be integer and the length of vectors in $v_x$ is the same as in $v_y$; its \CFunction is the following constraint: the mapping $\{ v_x \mapsto g_x, v_y \mapsto g_y \}$ is a solution iff $g_x \in G_x, g_y \in G_y$ ($G_x \in \groups, G_y \in \groups$) and each value in $g_x$ has the rank (possibly with ties) specified in $g_y$.

The constraint \textit{rank} has
\begin{itemize}
\item \CName = \textit{$g_Y$ = RANK($g_X$)}, where $g_X$ and $g_Y$ are the group variables;
\item \CSignature = subgroup $g_X$ (associated with X) is numeric, $g_Y$ is integer and the length of vectors in $g_X$ is the same as in $g_Y$; and
\item
\CFunction = \textit{$g_Y$ = RANK($g_X$)} iff $g_X \in G_X, g_Y \in G_Y$ and each value in $g_X$ has the rank (possibly with ties) specified in $g_Y$.
\end{itemize}

@@

\sergey{Table should take into account our new notation and balance between formality and intuition, heh}
\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{XXX}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    \ecalldiff{v_x} & $\integer{v_x}$ or $\textual{v_x}$ & All elements in $v_x$ are different \\
    %X = Y & & \\
    \ecfkey{v_{fk}}{v_{pk}} & FK and PK have the same type; they originate from different tables and PK is all-different & all values in FK exist in PK \\
    % TODO check out
    \eclookupprod{v_r}{v_1}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \eclookup{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \eclookupfuzzy{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecperm{v_x} & & \\
    \ecprod{v_r}{v_1}{v_2} & & \\
    \ecproj{v_r}{\mathbf{v_x}} & & \\
    \ecrank{v_r}{v_1} & Y and X have the same length & Y is the rank of X (including ties)\\
    \ectotal{v_r}{v_{pos}}{v_{neg}} & A, P and N have the same length and their length is at least 2 & *\\
    \ecseries{v_x} & & \\
    \ecsumc{v_r}{\mathbf{v_x}} & & Y is the result of summing each column in X \\
    \ecsumr{v_r}{\mathbf{v_x}} & & Y is the result of summing each row in X \\
    \ecsumif{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecsumprod{v_r}{v_1}{v_2} & & \\

@@

For every spreadsheet a ground-truth has been provided manually, specifying the essential (or original) constraints that are expected to be discovered.
We consider three types of constraints:
\begin{description}
  \item[Implemented] Constraint that have been implemented and are expected to be found
  \item[Essential] Constraint that have or have not been implemented but could be found using our algorithm
  \item[Non-trivial] Constraints currently outside of the scope of this system (e.g. generic nested mathematical or logical formulas or n-ary constraints)
\end{description}

>>>>

\paragraph{Example}
\sergey{need to use this below:}
  For example, a spreadsheet constraint \textit{rank} has \CName \textit{$v_r$ = RANK($v_x$)}, where $v_x$ and $v_r$ are its variables; its \CSignature is: groups assigned to $v_x$ must be numeric, groups assigned to $v_y$ must be integer and the length of vectors in $v_x$ is the same as in $v_y$; its \CFunction is the following constraint: the mapping $\{ v_x \mapsto G_x', v_y \mapsto G_y' \}$ is a solution iff $G_x' \subset G_x, G_y' \subset G_y$ ($G_x \in \groups, G_y \in \groups$) and each value in $G_y'$ is the rank of the corresponding value in $G_x'$ (possibly with ties).

%The constraint \textit{rank} has
%\begin{itemize}
%\item \CName = \textit{$v_r$ = RANK($v_x$)}, where $v_r$ and $v_x$ are %the variables;
%\item \CSignature = subgroup $g_X$ (associated with X) is numeric, $g_Y$ %is integer and the length of vectors in $g_X$ is the same as in $g_Y$; and
%\item
%\CFunction = \textit{$g_Y$ = RANK($g_X$)} iff $g_X \in G_X, g_Y \in G_Y$ %and each value in $g_X$ has the rank (possibly with ties) specified in $%g_Y$.
%\end{itemize}

@@

\sergey{Table should take into account our new notation and balance between formality and intuition, heh}
\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{XXX}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    \ecalldiff{v_x} & $\integer{v_x}$ or $\textual{v_x}$ & All elements in $v_x$ are different \\
    %X = Y & & \\
    \ecfkey{v_{fk}}{v_{pk}} & FK and PK have the same type; they originate from different tables and PK is all-different & all values in FK exist in PK \\
    % TODO check out
    \eclookupprod{v_r}{v_1}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \eclookup{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \eclookupfuzzy{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecperm{v_x} & & \\
    \ecprod{v_r}{v_1}{v_2} & & \\
    \ecproj{v_r}{\mathbf{v_x}} & & \\
    \ecrank{v_r}{v_x} & Y and X have the same length & Y is the rank of X (including ties)\\
    \ectotal{v_r}{v_{pos}}{v_{neg}} & A, P and N have the same length and their length is at least 2 & *\\
    \ecseries{v_x} & & \\
    \ecsumc{v_r}{\mathbf{v_x}} & & Y is the result of summing each column in X \\
    \ecsumr{v_r}{\mathbf{v_x}} & & Y is the result of summing each row in X \\
    \ecsumif{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecsumprod{v_r}{v_1}{v_2} & & \\

@@

For every spreadsheet a ground-truth has been provided manually, specifying the essential (or original) constraints that are expected to be discovered.
We consider three types of constraints:
\begin{description}
  \item[Implemented] Constraint that have been implemented and are expected to be found (all constraints in Table~\ref{table:constraints})
  \item[Essential] Constraint that have or have not been implemented but could be found using our algorithm (e.g. fuzzy conditional sum)
  \item[Non-trivial] Constraints currently outside of the scope of this system (e.g. generic nested mathematical or logical formulas or n-ary constraints)
\end{description}
